\begin{discussion}
  We are going to state the governing laws for the discrete heat transport
  phenomenon in the strong formulation.

  Let:
  \begin{itemize}
    \item $D$ be a positive integer (physical dimension);
    \item $M$ be a manifold-like flat mesh of dimension $D$;
    \item $K$ be the Forman subdivision of $M$;
    \item $t_0 \in \R$ be the initial time, $I = [t_0, \infty)$.
  \end{itemize}
  Physical quantities in our model are:
  \begin{itemize}
    \item
      temperature $u [\Theta] \colon I \to C^0 K$;
    \item
      heat energy density $\tilde{Q} [E L^{-D}] \colon I \to C^0 K$;
    \item
      dual heat flow rate $\tilde{q} [E L^{1 - D} T^{-1}] \colon I \to C^1 K$;
  \end{itemize}
  The governing laws are the following.
  \begin{itemize}
    \item
      Let
        $K' := K \setminus \partial K$ be the interior of $K$,
        $\tilde{f} [E L^{-D} T^{-1}]\in C^0 K'$
        be the dual internal production rate;
      \textbf{Conservation of heat energy} is modeled by the equation
      \begin{equation}
        \restrict{\frac{\partial \tilde{Q}}{\partial t}}{K'_0} =
        \restrict{(\delta_1^\star \tilde{q})}{K'_0} + \tilde{f}.
      \end{equation}
    \item
      Let $u_0 [\Theta] \in C^0 K$ be the initial temperature.
      The \textbf{initial condition} is given by prescribed initial temperature:
      \begin{equation}
        u(t_0, \cdot) = u_0.
      \end{equation}
    \item
      Let $\tilde{\pi} [E L^{-D} \Theta^{-1}] \colon C^0 K \to C^0 K$
      be the dual volumetric heat capacity
      (its matrix in the standard basis is diagonal).
      The \textbf{relation between temperature change and heat energy change}
      is given by
      \begin{equation}
        \frac{\partial \tilde{Q}}{\partial t}
        = \tilde{\pi} \frac{\partial u}{\partial t}.
      \end{equation}
    \item
      Let
      $\tilde{\kappa} [E L^{2 - D} T^{-1} \Theta^{-1}] \colon C^1 K \to C^1 K$
      be the dual thermal conductivity
      (its matrix in the standard basis is diagonal).
      The \textbf{Fourier's constitutive relation} is given by
      \begin{equation}
        \tilde{q} = - \tilde{\kappa} (\delta_0 u).
      \end{equation}
  \end{itemize}
  We complete our model with boundary conditions.
  Let $\Gamma_D, \Gamma_N$ form a partition of $\partial K$
  into Dirichlet and Neumann boundary.
  \begin{itemize}
    \item
      Let $g_D [\Theta] \colon I \to C^0 \Gamma_D$
      be the prescribed temperature on the Dirichlet boundary $\Gamma_D$.
      The \textbf{Dirichlet boundary condition} is given by
      \begin{equation}
        \restrict{u}{\Gamma_D} = g_D.
      \end{equation}
    \item
      Let
        ${\bf n} [L^{-1}] \colon \Gamma_N \to \R^d$
          be the generalized exterior unit normal,
        $\widetilde{g_N} [E L^{1 - D} T^{-1}] \colon I \to C^0 \Gamma_N$
          of physical dimension $[E L^{1 - D} T^{-1}]$
          be the prescribed dual flow rate through the Neumann boundary.
      The \textbf{Neumann boundary condition} is given by
      \begin{equation}
        \restrict{\overline{\tilde{q}}}{\Gamma_N} \cdot {\bf n}
        = \widetilde{g_N}.
      \end{equation}
  \end{itemize}
\end{discussion}
