\begin{definition}
  Let $\mathcal{C}$ and $\mathcal{D}$ be categories.
  A \textbf{functor} $F$ is a pair $(F_{\rm Obj}, F_{\rm Mor})$, where
  $F_{\rm Obj} \colon {\rm Obj}_{\mathcal{C}} \to {\rm Obj}_{\mathcal{D}}$ and
  $F_{\rm Mor} \colon {\rm Mor}_{\mathcal{C}} \to {\rm Mor}_{\mathcal{D}}$
  and the following conditions are satisfied.
  \begin{enumerate}
    \item
      \textbf{$F$ maps domains and codomains accordingly.}
      For any $f \in {\rm Mor}_{\mathcal{C}}$,
      \begin{subequations}
        \begin{alignat}{1}
          & {\rm Domain}_{\mathcal{D}}(F_{\rm Mor} f)
          = F_{\rm Obj}({\rm Domain}_{\mathcal{D}} f), \\
          & {\rm Codomain}_{\mathcal{D}}(F_{\rm Mor} f)
          = F_{\rm Obj}({\rm Codomain}_{\mathcal{D}} f).
        \end{alignat}
      \end{subequations}
    \item
      \textbf{$F$ respects identities.}
      For any $X \in {\rm Obj}_{\mathcal{C}}$,
      \begin{equation}
        F_{\rm Mor} \id_X = \id_{F_{\rm Obj} X}
      \end{equation}
    \item
      \textbf{$F$ respects composition.}
      for any $f, g \in {\rm Mor}_{\mathcal{C}}$, with
      ${\rm Domain} g = {\rm Codomain} f$,
      \begin{equation}
        F(g \circ f) = F g \circ F f.
      \end{equation}
  \end{enumerate}
  It is a common convention to abuse the notation and use the single symbol $F$
  for both $(F_{\rm Obj}$ and $F_{\rm Mor})$.
\end{definition}
\begin{example}[Forgetful functors]
  Let $\mathcal{C}$ be a category of algebraic structures
  (e.g., groups, rings, modules, etc.).
  We define the forgetful functor $F$ as follows: it maps an algebraic structure
  to its carrier set (e.g., the group $(\R, +, -, 0)$ to the set $\R$) and a
  mrphism to itself.
  All the conditions for a functor are trivially satisfied.
\end{example}
\begin{example}[Power-set functor]
  In the category of sets consider the endofunctor
  $F = (F_{\rm Obj}, F_{\rm Mor})$ defined as follows.
  For a set $X$ define $F_{\rm Obj}(X) = \mathcal{P} X$ and for a function
  $f \colon X \to Y$ define $F f \colon \mathcal{P} X \to \mathcal{P} Y$ by
  \begin{equation}
    A \in \mathcal{P} X
    \mapsto (F f) A := \set{f(x)}{x \in A} \in \mathcal{P} Y.
  \end{equation}
\end{example}
