\begin{definition}
  Let $(G, e, \iota, \mu)$ be a group with a manifold structure on it.
  We say that $G$ is a \textbf{Lie group} if
  the multiplication $\mu \colon G \times G \to G$ and
  the inversion $\iota \colon G \to G$
  are smooth functions.
\end{definition}
\begin{definition}
  Let $G$ be a Lie group.
  For any $g \in G$ define the left action $L_g \colon G \to G$ as follows:
  for any $h \in G$, $L_g h = g h$.
  We say that a vecctor field $X$ on $G$ is \textbf{left-invariant} if for any
  $g, h \in G$,
  \begin{equation}
    (d L_g) \restrict{X}{h} = \restrict{X}{g h}.
  \end{equation}
  Denote the space of left-invariant vector fields on $G$ by ${\rm Left}(G)$.
\end{definition}
\begin{proposition}
  Let $G$ be a Lie group.
  Then ${\rm Left}(G)$ is a Lie subalgebra of the Lie algebra of vector fields.
\end{proposition}
\begin{proposition}
  Let $G$ be a Lie group.
  Define the map $f \colon {\rm Left}(G) \to T_e G$ as
  \begin{equation}
    f(X) := \restrict{X}{e},\ X \in {\rm Left}(G)
  \end{equation}
  Then $f$ is a linear isomorphism.
\end{proposition}
\begin{definition}
   Let $G$ be a Lie group.
   Define $\mathfrak{g} := T_e G$.
   For $X, Y \in \mathfrak{g}$ define (using the map $f$ from above)
   \begin{equation}
     \lie{X}{Y} := \lie{f^{-1} X}{f^{-1} Y},
   \end{equation}
   where the right Lie bracket is the standard Lie bracket on vector fields.
   In other words, the Lie bracket structure on ${\rm Left}(G)$ is transported
   to a Lie algebra structure on $\mathfrak{g}$.
   The Lie algebra $\mathfrak{g}, \lie{\cdot}{\cdot}$ is called the
   \textbf{Lie algebra of the Lie group} $G$.
\end{definition}
\begin{definition}
  Let $G$ be a Lie group with a Lie algebra $\mathfrak{g}$.
  Define the \textbf{exponential map} $\exp \colon \mathfrak{g} \to G$
  as folows: for any $X \in \mathfrak{g}$, let $\gamma_X \colon \R \to G$ be the
  unique one-parameter subgroup of $G$ whose tangent vector at the identity is
  equal to $X$.
  Then
  \begin{equation}
    \exp X := \gamma_X(1).
  \end{equation}
\end{definition}
