\begin{definition}
  Let
    $R$ be a commutative ring with unity,
    $A$ be an $R$-algebra,
    $D \in \Hom_R(A, A)$.
  We say that $D$ is a \textbf{derivation} if for any $a, b \in A$ the
  \textbf{Leibniz rule} (or the \textbf{product rule}) holds:
  \begin{equation}
    D(a * b) = (D a) * b + a * (D b).
  \end{equation}
  By ${\rm Der}_A$ we will denote the set of all derivations.
\end{definition}
\begin{example}[Derivative of a single variable function is derivation]
  Let
    $R = \R$,
    $A = C^\infty(\R)$ be the space of infinitely differentiable functions,
    $D$ is the derivative operator, i.e., $D f = f'$ for $f \in A$.
  Then $D$ is derivation.
\end{example}
\begin{example}
  Let $R$ be a commutative ring with unity,
  $V$ be a Lie algebra over $R$.
  Then the adjoint homomorphism ${\rm adj} \colon V \to {\rm End}_V$ induces for
  each $x \in V$ a derivation ${\rm adj}_x \colon V \to V$.
  Indeed, take $x, y, z \in A$.
  Then
  \begin{equation}
    {\rm adj}_x [y, z]
    = [x, [y, z]]
    = - [z, [x, y]] - [y, [z, x]]
    = [[x, y], z] + [y, [x, z]]
    = [{\rm adj}_x y, z] + [y, {\rm adj}_x z].
  \end{equation}
\end{example}
\begin{proposition}
  Let $R$ be a commutative ring with unity,
  $A$ be a unital, commutative, and associative $R$-algebra.
  Then ${\rm Der}_A$ is an $A$-module under pointwise addition and
  multiplication with a scalar.
\end{proposition}
\begin{proof}
  Let $D, D_1, D_2 \in {\rm Der}_A$.
  Then $D_1 + D_2$ is a homomorphism from module theory.
  To prove it satisfies the Leibniz rule, let $a, b \in A$.
  Then
  \begin{equation}
    (D_1 + D_2)(a * b)
    = D_1(a * b) + D_2(a * b)
    = D_1 a * b + a * D_1 b + D_2 a * b + a * D_2 b
    = (D_1 + D_2) a * b + a * (D_1 + D_2) b.
  \end{equation}
  Further, let $a \in A$.
  Then $(a \cdot D)(b) := a * D b$ for any $b \in B$.
  It is trivial to check it it is a homomorphism.
  To check it is a derivation, let $b, c \in A$.
  Then
  \begin{equation}
    (a \cdot D)(b * c)
    = a * D(b * c)
    = a * (D b * c + b * D c)
    = (a * D b) * c + b * (a * D c)
    = (a \cdot D) b * c + b * (a \cdot D) c. 
  \end{equation}
  Hence, ${\rm Der}_A$ is an $A$-module.
\end{proof}
\begin{proposition}
  Let $R$ be a commutative ring with unity,
  $A$ be a unital, commutative, and associative $R$-algebra,
  $X, Y \in {\rm Der}_A$.
  Then $X \circ Y - Y \circ X \in {\rm Der}_A$.
\end{proposition}
\begin{corollary}
  Let $R$ be a commutative ring with unity,
  $A$ be a unital, commutative, and associative $R$-algebra.
  Then ${\rm Der}_A$ is a Lie algebra with Lie bracket given by
  \begin{equation}
    [X, Y] := X \circ Y - Y \circ X,\ X, Y \in {\rm Der}_A. 
  \end{equation}
\end{corollary}
